Return of the Linguist:\\Toward scalable parallel corpus generation for machine translation

### 2016-06-28 doc/paper.tex
added MultEval tables

For the rest of this section, we show the results of applying the same post-editing procedure to the test and training sets as well, with the additional step of restoring missing segments for both languages. 
To preserve the integrity of {\small \tt tst2014}, evaluation is now performed using MultEval \mycitep{multeval} on the {\small \tt tst2010} data set itself, with the MERT procedure tuned on the {\small \tt dev2010} data set instead.
These are the data sets and evaluation software used by the official benchmark cited in footnote \ref{foot:tst2010}.
MultEval has the added benefit of providing bootstrapped error bar estimates.

% TODO TODO TODO: rerun these jobs with GIZA++ instead of mgiza! TINY difference in error bars, but should try to be as careful as possible
    % I suppose I MIGHT consider this if the paper is ACCEPTED, haha
\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{2}{*}{BLEU $\uparrow$}
& baseline & 11.5 & 0.3 & - & - \\
& system 1 & 10.9 & 0.3 & - & 0.00 \\
\hline
\multirow{2}{*}{TER $\downarrow$}
& baseline & 76.0 & 0.8 & - & - \\
& system 1 & 82.8 & 1.0 & - & 0.00 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}
\caption{\label{tab:scores} Metric scores for all systems generated using MultEval 0.5.1 \mycitep{multeval}: jBLEU V0.1.1 (an exact reimplementation of NIST's mteval-v13.pl without tokenization); Translation Error Rate (TER) V0.8.0. p-values are relative to baseline and indicate whether a difference of this magnitude (between the baseline and the system on that line) is likely to be generated again by some random process (a randomized optimizer). Metric scores are averages over multiple runs. $s_{sel}$ indicates the variance due to test set selection and has nothing to do with optimizer instability.}
\end{table}

Input-domain noise can play a role similar to regularization in machine learning - get a reference from denoising autoencoders?
We do indeed find that making the tuning set translations more literal also tends to decrease performance, but this could be because of premature stopping.
Also, the amount of noise added is generally some small amount of Gaussian noise, and it is unclear

For tst2014, revising the DEV set tst2010 instead leads to different local minima instead. 
A better explanation is that the effect of this amount and kind of noise is ill-defined.

% Data Snooping - dedicate this to its own section, to make clear that these are not ``REAL'' results
% we perform snooping on a dedicated snooping set (as if that makes it right...)

>>>>

For the rest of this section, we show the results of applying the same post-editing procedure to the test and training sets as well, with the additional step of restoring missing segments for both languages. 
To preserve the integrity of {\small \tt tst2014}, evaluation is now performed using MultEval \mycitep{multeval} on the {\small \tt tst2010} data set itself, with the MERT procedure tuned on the {\small \tt dev2010} data set instead.
Our baseline model is also trained on the IWSLT corpus Chinese-English training corpus from 2014 instead of 2015.
These data sets and this evaluation software were used by the official benchmark cited in footnote \ref{foot:tst2010}.
MultEval has the added benefit of providing bootstrapped error bar estimates.

% TODO: I am here. the rest of the stuff from here to ``Proposed Future Work'' is not finished yet. Just draft entries...

% In Table~\ref{tab:multeval_tst2010} 
In the tables below with MultEval results, metric scores for all systems were generated using MultEval 0.5.1 \mycitep{multeval}: jBLEU V0.1.1 (an exact reimplementation of NIST's mteval-v13.pl without tokenization); Translation Error Rate (TER) V0.8.0. 
The $p$-values are relative to the baseline and indicate whether a difference of this magnitude (between the baseline and the system on that line) is likely to be generated again by some random process (a randomized optimizer). 
Metric scores are averages over three runs per system. 
$s_{sel}$ indicates the variance due to test set selection and has nothing to do with optimizer instability.\footnote{
    This paragraph and the tables with MultEval results are adopted from \LaTeX~code automatically generated by MultEval.
}

% \pagebreak % soooooo ugly

% well, looks like I'm stuck doing discussion THEN table... (tab:multeval_tst2010 won't fit on the same page if before)
Let's discuss Table~\ref{tab:multeval_tst2010}.
Train2015 adds more data, but it's noisy and does not produce a statistically significant change in scores.
On the other hand, post-edited {\small \tt train2015} produces a significant improvement in scores.
(Quality matters - not just quantity, which is something we've been saying. Post-editing makes a significant difference.)
% TODO: post-editing DOES provide performance boost. But it's labor intensive, and a SMALL boost...
Unlike Table~\ref{tab:tst2010}, post-editing the MERT tuning set {\small \tt dev2010} actually makes things uniformly worse.
The effect of this kind of noise in tuning corpora appears to be ill-defined.
Input-domain noise can play a role similar to regularization in machine learning - get a reference from denoising autoencoders?
We do indeed find that making the tuning set translations more literal also tends to decrease performance, but this could be because of premature stopping.
Also, the amount of noise added is generally some small amount of Gaussian noise, and it is unclear

\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{5}{*}{BLEU $\uparrow$}
& Official IWSLT14 baseline  & 11.2 & -   & -   & - \\
& Our baseline & 11.4 & 0.3 & 0.2 & - \\
& Trained on 2015 corpus ({\small \tt train2015}) & 11.5 & 0.3 & 0.3 & 0.30 \\
& Post-edited: {\small \tt train2015} & \textbf{11.7} & 0.3 & 0.1 & 0.01 \\
& Post-edited: {\small \tt dev2010} & 10.8 & 0.3 & 0.3 & 0.00 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & 11.0 & 0.3 & 0.2 & 0.00 \\
\hline
\multirow{5}{*}{TER $\downarrow$}
& Official IWSLT14 baseline & 77.0 & -   & -   & - \\
& Our baseline & 76.2 & 0.8 & 0.3 & - \\
& Trained on {\small \tt train2015} & 76.4 & 0.8 & 0.5 & 0.26 \\
& Post-edited: {\small \tt train2015} & \textbf{75.6} & 0.8 & 0.0 & 0.00 \\
& Post-edited: {\small \tt dev2010} & 83.4 & 1.0 & 0.5 & 0.00 \\
%& system 4 & 82.7 & 1.0 & 0.8 & 0.00 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}

\caption{\label{tab:multeval_tst2010} % \caption[LoF entry] would allow multi-paragraph caption... \hspace{0.6 cm} to indent
%\-\caption[LoF entry]{ \label{tab:multeval_tst2010}
MultEval results for systems evaluated on the unmodified {\small \tt tst2010} data set.
Official baseline results (with IRSTLM instead of KenLM as discussed previously) are also given for comparison.
%UHHHH do I have anything else to say here in the immediate caption? 
%I'll interpret results in the text body.
%But this caption needs to be kind of short, because otherwise it winds up on a different page than its discussion... although at this rate, it doesn't really matter - that'll happen anyway
} % caption
\end{table}

% TODO: Adding train2015 + 
% this is pointless to say, unless I also have unmodified train2015 + dev2010?

\pagebreak
Now we discuss Table~\ref{tab:multeval_tst2010-fixed}.
This time there is a statistically significant improvement in TER for train2015, but not for BLEU.
Post-editing train2015 again leads to further improvement.
More surprisingly, post-edited dev2010 gets slightly better BLEU at the expense of much worse TER; this is more like Table~\ref{tab:tst2010} than Table~\ref{tab:multeval_tst2010}.
This is counter-intuitive, since you would think that removing sentences with duplicated segments from tst2010 would improve TER scores, not worsen them.
This emphasizes the fact that tuning set noise can affect bottom-line performance in relatively unpredictable ways.

\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System (all with post-edited {\small \tt tst2010}) & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{5}{*}{BLEU $\uparrow$}
& Our baseline & 11.4 & 0.3 & 0.2 & - \\
& Trained on {\small \tt train2015} & 11.4 & 0.3 & 0.2 & 0.44 \\
& Post-edited: {\small \tt train2015} & 11.6 & 0.3 & 0.2 & 0.01 \\
& Post-edited: {\small \tt dev2010} & \textbf{11.9} & 0.3 & 0.1 & 0.00 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & \textbf{12.2} & 0.3 & 0.1 & 0.00 \\
\hline
\multirow{5}{*}{TER $\downarrow$}
& Our baseline & 70.6 & 0.4 & 0.5 & - \\
& Trained on {\small \tt train2015} & 70.1 & 0.4 & 0.3 & 0.00 \\
& Post-edited: {\small \tt train2015} & \textbf{69.7} & 0.4 & 0.2 & 0.00 \\
& Post-edited: {\small \tt dev2010} & 75.1 & 0.5 & 0.3 & 0.00 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & 74.7 & 0.5 & 0.2 & 0.00 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}

\caption{\label{tab:multeval_tst2010-fixed} % \caption[LoF entry] would allow multi-paragraph caption... \hspace{0.6 cm} to indent
%\-\caption[LoF entry]{ \label{tab:multeval_tst2010}
MultEval results for systems evaluated on the post-edited {\small \tt tst2010} data set.
} % caption
\end{table}

\subsection{Data Snooping}
% Data Snooping - dedicate this to its own section, to make clear that these are not ``REAL'' results
we perform snooping on a dedicated snooping set (as if that makes it right...)

uhhh there's not enough room for a table and discussion, is there? i guess i'd have to pad with some philosophical discussion about snooping

\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{3}{*}{BLEU $\uparrow$}
& baseline & 11.4 & 0.3 & 0.2 & - \\
& system 1 & 36.8 & 0.6 & 0.0 & 0.00 \\
& system 2 & 11.2 & 0.3 & 0.1 & 0.03 \\
\hline
\multirow{3}{*}{TER $\downarrow$}
& baseline & 76.2 & 0.8 & 0.3 & - \\
& system 1 & 48.3 & 0.7 & 0.0 & 0.00 \\
& system 2 & 76.3 & 0.7 & 0.1 & 0.46 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}

\caption{\label{tab:multeval_tst2010-fixed} % \caption[LoF entry] would allow multi-paragraph caption... \hspace{0.6 cm} to indent
%\-\caption[LoF entry]{ \label{tab:multeval_tst2010}
MultEval results for systems evaluated on the post-edited {\small \tt tst2010} data set.
System 1: trained on the concatenation of train14 and tst2010. SNOOPING!
System 2: snooped out a bunch of mistranslated or OOV words from baseline translation and generated sentences with those words using the generator (remember that thing?)
} % caption
\end{table}

The rationale for not bothering with tmcombine was that the additional data was very small in comparison.
Shouldn't skew the tables that much or whatever.
Yet there is still the ``unreasonable effectiveness of data'' or whatever - but really it's just overfitting...

Snooping data set establishes an ``upper bound'' of sorts of how much performance boost you could get by simply adding more data.
It's a measure of the inherent limitation (bias?) of the model being used.
Generated data doesn't make a dent, and in fact makes things slightly worse (although TER is within error bars).
So nonsense sentences of OOV words does NOT help - or even if it does, the nonsense-noise drowns it out
